Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-02-05 man/figures/std_anomalies.Rmd
add more ticks

---
output:
  word_document
---

@@

**Figure 2.** EVI standardized anomaly during the period 2000-2016 for northern and southern populations. Error bars show standard error.

@@

plot_sa_clu  <- avg_sa_clu %>%  
  ggplot(aes(x=y, y=mean, fill=signo)) + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se, colour=signo), width=.5) +
  facet_wrap(~clu_pop2, nrow = 2) + 
  scale_fill_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  scale_color_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  ylab(myylab) + xlab('') +
  theme_bw() +
  theme(text = element_text(size=12),
        legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = -0.05, size = 12, 
                                    margin = margin(t=-5, b=1)))
```

>>>>

---
output:
  word_document
editor_options: 
  chunk_output_type: console
---

@@

**Figure 2.** EVI standardized anomaly during the period 2000-2016 for northern and southern populations. Error bars show standard error. See main text for details on EVI calculation.

@@

plot_sa_clu  <- avg_sa_clu %>%  
  ggplot(aes(x=y, y=mean, fill=signo)) + 
  geom_hline(yintercept = 0, size=0.3, colour = "gray") + 
  geom_bar(stat = "identity") + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se, colour=signo), width=.5) +
  facet_wrap(~clu_pop2, nrow = 2) + 
  scale_fill_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  scale_color_manual(values = c("pos" = color_pos, "neg" =  color_neg)) +
  scale_x_continuous(breaks = seq(2000, 2016, by=2)) +
  ylab(myylab) + xlab('Year') +
  theme_bw() +
  theme(axis.text = element_text(size=8),
        legend.position = "none",
        panel.grid = element_blank(),
        strip.background = element_rect(fill = "transparent", colour = "black", size = 0.2),
        plot.title = element_text(hjust = -0.05, size = 9, 
                                    margin = margin(t=-5, b=1)))
```
